---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fertile: creating optimal conditions for reproducibility 

The goal of `fertile` is to make creating a reproducible project as easy as possible, for users of all levels of sophistication.

## Installation

You can install fertile from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("beanumber/fertile")
```

## Example

From within any R project directory, check your work for reproducibility:

```{r example, eval=FALSE}
ferile::check()
```

## Implementation

### Stage 1 (fall 2018)

- Implement `check()` for diagnosing and cleaning up an existing codebase
    - modeled on `devtools::check()` and `goodpractice::gp()`
    - Diagnostic part
        - scans code files and finds potentiall bad paths
        - checks URLs to ensure they are valid/active
        - checks DBI connections
        - scans project directory (recursively) and suggests re-organization of files
        - grep on file extensions and probably scan through text files
    - Fix part
        - fixes paths to be relative to project root (`here::here()`)
        - move `data` to `data/`
        - move code to `R/`, or `Rmd/` (or `src/` ?)
        - move other crap to `inst/`

### Stage 2 (spring 2019)

- Implement some kind of painless `make`-like functionality
- See also: [easyMake](https://github.com/GShotwell/easyMake), [drake](https://github.com/RobotLocomotion/drake)

### Stage 3 (?)

- Self-bundling
- Certification
