---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(fertile)
library(tidyverse)
```

[![Travis-CI Build Status](https://travis-ci.org/baumer-lab/fertile.svg?branch=master)](https://travis-ci.org/baumer-lab/fertile)

# fertile: creating optimal conditions for reproducibility 

The goal of `fertile` is to make creating a reproducible project as easy as possible, for users of all levels of sophistication.

`fertile` provides a wide variety of checks that can be run on your project to test different aspects of its reproducibility--including clean project structure, portability of paths, and use of randomnes--as well as several functions that will create reproducibility reports for you with information about referenced packages and file paths.

## Installation

You can install `fertile` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("baumer-lab/fertile")
```

## Reproducibility Reports

From within any R project directory, you can create a report of reproducibility with `proj_test()` or its smaller component functions.

This report will contain information about packages referenced in project code, files in your directory and suggestions for reorganizing them, as well a list of absolute and/or non-portable paths passed to functions in your code.

```{r example 1, warning = FALSE}
proj_test("tests/testthat/project_noob/")
```

## Reproducibility Checks

There are several functions allowing you to run checks on project reproducibility. 

The function `proj_check()` runs 16 different tests to check your project for reproduciblity, and provides a summary of checks that you passed as well as ones to work on and how to improve them. Each of these checks can also be run individually.

`proj_check_some()` will complete a selection of the checks run by `proj_check()`, specified by the user through a `dplyr::select`-style statement. 

```{r example 2, warning = FALSE, message = FALSE}
proj_check_some("tests/testthat/project_miceps", contains("tidy"), ends_with("root"), has_only_used_files)
```


`fertile` has two modes: 

- diagnostic or retrospective
- interactive or prospective


Reproducibility reports and checks make up the diagnostic part of `fertile`. The interactive component comes from a system of path logging:


## Logging and Reporting of Paths

When you have fertile loaded, the package will interactively edit a log file located in your project directory, which will record the paths/arguments passed to commonly-used input and output functions that you execute in files or in the console. You can access this file using `log_report()`, which reads the log, and `log_clear()`, which erases the log and starts it over.

```{r example 3, message = FALSE, warning = FALSE}
log_clear()
library(mime)
library(fertile)
set.seed(10)
read.csv("tests/testthat/data/data.csv")
log_report()
```

```{r example 4, message = FALSE}
log_clear()
log_report()
```

The retrospective functions `proj_check()`, `proj_check_some()`, `proj_test()`, and the functions related to them harness this same logging system to produce reports. However, all editing of the interactive log is independent from the retrospective log, which is not user-accessible.


## Implementation

### Stage 1 

- Implement `proj_check()` for diagnosing and cleaning up an existing codebase
    - modeled on `devtools::check()` and `goodpractice::gp()`
    - Diagnostic part
        - scans code files and finds potentially bad paths
        - checks URLs to ensure they are valid/active
        - checks DBI connections
        - scans project directory (recursively) and suggests re-organization of files
        - grep on file extensions and probably scan through text files
    - Fix part
        - fixes paths to be relative to project root (`here::here()`)
        - move `data` to `data/`
        - move code to `R/`, or `Rmd/` (or `src/` ?)
        - move other crap to `inst/`

### Stage 2 

- Implement some kind of painless `make`-like functionality
- See also: [easyMake](https://github.com/GShotwell/easyMake), [drake](https://github.com/ropensci/drake)

### Stage 3 

- Self-bundling
- Certification
