---
title: "`fertile` for Reproducibility"
author: "Ben Baumer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{`fertile` for Reproducibility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
Sys.setenv("IN_TESTTHAT" = TRUE)
```

```{r load, message=FALSE}
library(readr)
library(fertile)
```

# fertile: creating optimal conditions for reproducibility 

## Goal

- Make creating a reproducible project as easy as possible, for users of all levels of sophistication

## Why do we need this?

- Creating an R package ensures some degree of quality control in the code, but is way too hard to for all but the most experienced R users. It's developer-centric.
- Most people, even experienced R users who value reproducibility, are terrible at actually creating reproducible data analysis projects
- Learning `make` is hard and maybe unnecessary
- Many journals now have reproducibility editors, but there is no standard or automated way to achieve reproducibility

## What is it? 

- `goodpractice`/`R CMD check` for data analysis projects

# Prospective Reproducibility

"I'm fiddling with pineapple coconut cake recipes,... 
 but I want someone else to be able to follow my steps."

Logs your actions

```{r read data, error=TRUE}
log_clear()
library(fs)

read_csv("data.csv")
read_csv("tests/testthat/data/data.csv")
log_report()
```

Checks paths

```{r write data, error=TRUE}
readr::read_csv("../fertile/tests/testthat/data/data.csv")
fertile::read_csv("../fertile/tests/testthat/data/data.csv")
read_csv(tempfile())

write_csv(data.frame(a = 1), file = tempfile())
write_csv(data.frame(a = 1), file = "temp_data.csv")
log_report()
```

Prevents you from doing bad things

```{r set directory, error=TRUE}
setwd("vignettes")
```

Works by shimming many I/O functions

```{r shims, eval=FALSE}
?shims
```


# Retrospective Reproducibility

"I've baked a pineapple cococnut cake. What was my recipe?"

- analyzes your code
- analyzes your files
- makes suggestions
- make moves

## A simple project

```{r open noob}
project_noob <- here::here("tests", "testthat", "project_noob")
fs::dir_info(project_noob)
```

Test it

```{r test noob, error=TRUE}
proj_test(project_noob)
```

## A slightly more complicated project

```{r open miceps}
project_miceps <- here::here("tests", "testthat", "project_miceps")
fs::dir_info(project_miceps)
```

```{r test miceps}
x <- proj_analyze(project_miceps)
x
```

```{r suggestions miceps, eval=FALSE}
proj_move_files(x$suggestions)
proj_suggest_moves(x$suggestions)
```


# Moving forward

- auto-detect unnecessary package loads
- `R CMD check` style checklist of potential problems
- Incorporate some of kind of `make`-inspired build chain
- Unfakeable certificate of reproducibility? 

# Questions

- Will this actually work?? Will it be useful for anyone?
- What recommendations to make about file structure? 
- How strict/opinionated to be? 
