---
subtitle: "`fertile` reproducibility report"
title: "Project: `r params$project_name`"
date: "`r Sys.time()`"
params:
  project_name: "miceps"
  awarded: !r c("structure", "paths")
  failed: !r c("tidy", "documentation", "randomness", "style")
  failures_structure: TRUE
  checks_structure: !r tibble::tibble()
  failures_tidy: TRUE
  checks_tidy: !r tibble::tibble()
  failures_documentation: TRUE
  checks_documentation: !r tibble::tibble()
  failures_paths: TRUE
  checks_paths: !r tibble::tibble()
  failures_randomness: TRUE
  checks_randomness: !r tibble::tibble()
  failures_style: TRUE
  checks_style: !r tibble::tibble()
  fullname: "N/A"
  username: "N/A"
  email: "N/A"
  github_username: "N/A"
  file_history: !r tibble::tibble()
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)
library(tidyverse)
library(knitr)
```


### Badges Awarded:

```{r, out.width="15%"}
img <- params$awarded %>%
  paste0("-badge.png") %>%
  system.file("help", "figures", ., package = "fertile")

knitr::include_graphics(img)
```


### Badges <span style='color: red;'>Failed:</span>

```{r, out.width="15%"}
img <- params$failed %>%
  paste0("-badge.png") %>%
  system.file("help", "figures", ., package = "fertile")

knitr::include_graphics(img)
```

---

```{r, eval = length(params$failed) > 0}
asis_output("### Reasons for Failure:")
```

```{r, eval = params$failures_structure}
asis_output("**Project Structure**")
params$checks_structure
```

```{r, eval = params$failures_tidy}
asis_output("**Tidy Files**")
params$checks_tidy
```

```{r, eval = params$failures_documentation}
asis_output("**Documentation**")
params$checks_documentation
```

```{r, eval = params$failures_paths}
asis_output("**File Paths**")
params$checks_paths
```

```{r, eval = params$failures_randomness}
asis_output("**Randomness**")
params$checks_randomness
```

```{r, eval = params$failures_style}
asis_output("**Code Style**")
params$checks_style
```

### Output Generation Details:

This project summary was generated on `r strsplit(as.character(Sys.time()), " ")[[1]][1]` at `r strsplit(as.character(Sys.time()), " ")[[1]][2]` (`r Sys.timezone()`)  by a user with the following information:

* Full name: `r params$fullname`
* Username: `r params$username`
* Email: `r params$email`
* GitHub Username: `r params$github_username`

The computer used to generate this file was running `r R.version.string` on the `r sessionInfo()$platform` platform and the `r sessionInfo()$running` operating system.

The files analyzed in the creation of this summary, as well as their last-modified timestamp, are provided below:

```{r}
params$file_history
```



---
